\LARGE \bf The TransHumUs project for the French Pavilion \\ at La Biennale di Venezia 2015

### 2015-08-28 docs/article.tex
dessin

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{When robotics meets art}
\subsection{The transHumUs project of Céleste Boursier-Mougenot}

@@

C/C institut français en anglais

@@

interpretation → discours sur le mouvement

@@

(en relation avec l’artiste)

\begin{itemize}
    \item feedback sur métabolisme
    \item arbre de 3t
    \item holonomie
    \item silence
    \item lenteur
    \item couverture spatiale
    \item coordination
\end{itemize}

@@

\begin{itemize}
    \item sondes Granier
    \item AGV tri-tourelles
    \item localisation absolue
\end{itemize}

@@

@@

\section{Implementation}
Photos

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tikz}
\usetikzlibrary{calc,patterns,angles,quotes,shapes}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    TODO
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{When robotics meets art}
\subsection{The transHumUs project of Céleste Boursier-Mougenot}

@@

For the 56th edition of the Venice Biennale International Contemporary Art Exhibit, Céleste Boursier-Mougenot composed a poetic work evoking the follies of 18th-century romantic parks, while revealing its political dimension.

With rêvolutions by artist Céleste Boursier-Mougenot, accompanied by the exhibit’s Curator, Emma Lavigne, the French Pavilion of the Venice Biennale has been transformed into an organic, dreamlike isle.

Under the glass roof, with the Pavilion’s flight and tree-lined lanes of the Giardini, Céleste Boursier-Mougenot has rolled out the choreography of three mobile trees moving according to their metabolism, the varying flow of their sap and their sensitivity when going from shadow to light.

@@

TODO interpretation → discours sur le mouvement

@@

Acording to the artist's wishes, we established the initial specifications for the piece of art, in order to find the right industrial partners:

\begin{itemize}
    \item The artwork will be composed by three trees of approximately 4 to 5 meters high and 3 tons;
    \item They will move in accordance with some feedback from their metabolism;
    \item The movement will be holonomic in a plane;
    \item The trees will have to move silently;
    \item The motion must be really slow, hardly perceptible (between 0 and 1 meter per minute);
    \item The trajectory shall cover as much as possible the available space;
    \item Several trees will have to coordinate themselves in the same area;
    \item The wheelbase must be able to roll on soft floors (mud and gravels) as well as on hard ones (concrete).
\end{itemize}

@@

\paragraph{Sapflow sensors} have been selected by biology researchers as they can provide a reliable signal correlated with the tree's metabolism.

\paragraph{Automatic Guided Vehicles} (AGV) with three directable wheels should comply with the admissible mechanical load on the concrete and provide an overall holonomic motion possibility.

\paragraph{Absolute geolocation} that works well indoor and outdoor, including on bumpy areas, at an affordable price is hard to find, but exists.

@@

As the artist wants an holonomic planar motion, in the most basic form, we need input 3 variables. The artist also wish that the trees behave in a similar manner in whatever direction it goes, so we choose a polar coordinate system concentric with the AGV: $(v, \theta, \omega)$, where:

\begin{itemize}
    \item $\theta \in [0, 2\pi[$ is the direction of the center of the AGV;
    \item $v \in [-1, 1]$ is its linear velocity along the direction $\theta$;
    \item $\omega \in [-1, 1]$ is its angular velocity.
\end{itemize}

With this system, we can easily compute the output needed by the AGV, which consist of the orientation $\theta_i$ of each wheel and its traction velocity $v_i$:

\begin{eqnarray*}
    v_{xi} &=& v \cos(\theta)- \omega \sin(\alpha_i) \\
    v_{yi} &=& v \sin(\theta)+ \omega \cos(\alpha_i) \\
    v_i &=& \sqrt{v_{xi}^2 + v_{yi}^2} \\
    \theta_i &=& \arctan(v_{yi}, v_{xi})
\end{eqnarray*}

\begin{figure}[thpb]
    \centering
    \begin{tikzpicture}
        \coordinate (o) at (0,0);
        \coordinate (v) at (0.5, {sqrt(3) / 2});
        \coordinate (x) at ({-sqrt(2) / 2}, {-sqrt(2) / 2});
        \coordinate (y) at ({+sqrt(2) / 2}, {-sqrt(2) / 2});
        \coordinate (z) at (0, 1);
        \draw (o) node [draw,thick,minimum size=4cm,name=O,regular polygon,regular polygon sides=8] {};
        \draw (O) node [fill=green,circle,draw,inner sep=1pt] {};
        \coordinate (a) at (O.side 2);
        \coordinate (b) at (O.side 4);
        \coordinate (c) at (O.side 7);
        \coordinate (d) at (O.side 6);
        \draw (a) node [fill=red,circle,draw,inner sep=1pt] {};
        \draw (b) node [fill=red,circle,draw,inner sep=1pt] {};
        \draw (c) node [fill=red,circle,draw,inner sep=1pt] {};
        \draw [->, red] (o) -- (v) node [above] {$v$};
        \draw [->, red] (a) -- ++(v) node [above] {$v$};
        \draw [->, red] (b) -- ++(v) node [left] {$v$};
        \draw [->, red] (c) -- ++(v) node [right] {$v$};
        \draw [->, blue] (a) -- ++(x) node [left] {$\omega R_2$};
        \draw [->, blue] (b) -- ++(y) node [pos=0.7, left] {$\omega R_3$};
        \draw [->, blue] (c) -- ++(z) node [pos=0.5, left] {$\omega R_1$};
        \draw [->] (a) -- ($ (a) + (v) + (x) $) node [left] {$v_2$};
        \draw [->] (b) -- ($ (b) + (v) + (y) $) node [right] {$v_3$};
        \draw [->] (c) -- ($ (c) + (v) + (z) $) node [above] {$v_1$};
        \draw [dashed] ($ (a) + (v) $) -- ($ (a) + (v) + (x) $);
        \draw [dashed] ($ (b) + (v) $) -- ($ (b) + (v) + (y) $);
        \draw [dashed] ($ (c) + (v) $) -- ($ (c) + (v) + (z) $);
        \draw [dashed] ($ (a) + (x) $) -- ($ (a) + (v) + (x) $);
        \draw [dashed] ($ (b) + (y) $) -- ($ (b) + (v) + (y) $);
        \draw [dashed] ($ (c) + (z) $) -- ($ (c) + (v) + (z) $);
        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_2$};
        \draw [blue] (o) -- (b) node [pos=0.5, below] {$R_3$};
        \draw [blue] (o) -- (c) node [pos=0.5, below] {$R_1$};
        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = c--o--v};
        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=75] {angle = d--o--c};
    \end{tikzpicture}
    \caption{$(v_i, \theta_i)$ as a function of $(v, \theta, \omega)$}
    \label{octogon}
\end{figure}

@@

\section{Implementation}

Photos
